A weakly structured stem for human origins in Africa

### 2023-03-02 paper.tex
more funding acknowledgements

We are grateful for the DNA contribution from each participant that enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for extensive data
visualization discussion and designing Figures \ref{fig:proposed-models} and
\ref{fig:best-fit-models}. This research was supported by CIHR project grant 437576,
Natural Sciences and Engineering Research Council of Canada (NSERC) grant RGPIN-2017-04816, 
and the Canada Research Chair program to SG. 
This research was supported by an NIH grant
R35GM133531 to BMH. The content is solely the responsibility of the authors
and does not necessarily represent the official views of the National
Institutes of Health. MM and EH acknowledge the support of the DSI-NRF Centre of Excellence for 
Biomedical Tuberculosis Research, South African Medical Research Council Centre for Tuberculosis 
Research, Division of Molecular Biology and Human Genetics, Faculty of Medicine and Health Sciences, 
Stellenbosch University, Cape Town, South Africa.

>>>>

We are grateful for the DNA contribution from each participant that enabled
this study; in particular we wish to highlight the generous participation of
the Richtersveld Nama community in South Africa and help from local research
assistants Willem DeKlerk and Hendrik Kaimann. Additional assistance and
community engagement was conducted by Justin Myrick, Chris Gignoux, Caitlen
Uren and Cedric Werely. We thank the African Genome Diversity Project for data
generation, including Tommy Carensten, Deepti Gurdasani, and Manj Sandhu. We
thank Luke Anderson-Trocm\'e and Georgette Femerling for assistance in creating
the map in Figure~\ref{fig:diversity} and Figure \ref{fig:toymodels},
respectively. We thank Nuria Melisa Morales-Garcia for extensive data
visualization discussion and designing Figures \ref{fig:proposed-models} and
\ref{fig:best-fit-models}. This research was supported by CIHR project grant 437576,
Natural Sciences and Engineering Research Council of Canada (NSERC) grant RGPIN-2017-04816, the Canada Research Chair program to SG, and the Canada Foundation for Innovation. 
This research was supported by an NIH grant
R35GM133531 to BMH. The content is solely the responsibility of the authors
and does not necessarily represent the official views of the National
Institutes of Health. MM and EH acknowledge the support of the DSI-NRF Centre of Excellence for 
Biomedical Tuberculosis Research, South African Medical Research Council Centre for Tuberculosis 
Research, Division of Molecular Biology and Human Genetics, Faculty of Medicine and Health Sciences, 
Stellenbosch University, Cape Town, South Africa.
